%-------------------------
% Resume in Latex
% Author : Anh Nguyen
% Based off of: Jake's Resume (https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% custom packages
\usepackage{ulem}
\input{glyphtounicode}
\usepackage{scrextend}
\usepackage[top=0.5in, left=0.5in, right=0.5in, bottom=0.5in]{geometry}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-0.7in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small#2} \\
      \textit{\small#3} & \textit{#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Anh Nguyen} \\ \vspace{1pt}
    \small (585) 309-9351 $|$
    \href{mailto:aln4739@rit.edu}{\uline{aln4739@rit.edu}} $|$ 
    \href{https://anhnlh.com}{\uline{anhnlh.com}} $|$
    \href{https://linkedin.com/in/anhnlh}{\uline{linkedin.com/in/anhnlh}} $|$
    \href{https://github.com/anhnlh}{\uline{github.com/anhnlh}} \\
    
\end{center}

%-----------SUMMARY-------------
\section{Summary}
\begin{addmargin}[0.15in]{0pt}
    Senior BS Computer Science at RIT with a focus on full-stack development, looking for a full-time Software Engineering position starting January 2025. Open to relocation.
\end{addmargin}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {\textbf{Honors Program}, BS Computer Science \& Economics}{Aug 2020 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{GPA:} 3.95/4.00}
        \resumeItem{\textbf{Coursework:} Artificial Intelligence, Machine Learning, Algorithms, Database Management, Distributed Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Amplify Education Inc.}{Brooklyn, NY (Remote)}
        {Software Engineer Co-op}{Jan 2024 -- Current}
        \resumeItemListStart
            \resumeItem{Working on xAPI (experience data collection) instrumentation within the student assessment platform.}
        \resumeItemListEnd
        \resumeSubSubheading
        {Software Engineer Co-op}{May 2022 -- Dec 2022}
        \resumeItemListStart
            \resumeItem{Built a student data merge tool for Tier 3 Support, reducing 15-30 minutes for each manual ticket resolution.}
            \resumeItem{Investigated data sources for the ongoing GraphQL integration, speeding up the overall transition process.}
            \resumeItem{Stood in as a Scrum Master for a sprint while the team's designated person was on leave.}
            \resumeItem{\textbf{Learned} cloud-based computing in AWS, front-end development in React, API development in GraphQL, service monitoring using DataDog, development patterns such as CI/CD, and numerous other skills.}
        \resumeItemListEnd
        
        \resumeSubheading
        {Rochester Institute of Technology}{Rochester, NY}
        {Student Lab Instructor}{Aug 2021 -- May 2022}
        \resumeItemListStart
            \resumeItem{Assisted the professor with delivering lessons and answering questions during lab sessions.}
            \resumeItem{Graded students' assignments and provided tutoring in the mentoring center.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{Languages:} Python, Java, C\#, SQL, JavaScript, TypeScript, Next.js \\
        %  \textbf{Database Systems:} PostgreSQL, DynamoDB, MongoDB \\ 
         \textbf{Developer Tools:} GitHub, Amazon Web Services (AWS), noSQL databases, Terraform, Docker, Cloudflare\\
        }}
    \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\normalem % toggle normal \emph
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\href{https://anhnlh.com}{\uline{\textbf{Self-hosted Portfolio}}} $|$ \emph{Linux, Cloudflare, Docker}}{Jan 2023 -- Current}
        \resumeItemListStart
            \resumeItem{Hosting my portfolio website along with the LoFiBeats project at \href{https://anhnlh.com}{\uline{anhnlh.com}}.}
            \resumeItem{\textbf{Utilized} Next.js for my website and Cloudflare to configure the domain and securely tunnel the personal server to the internet.}
        \resumeItemListEnd
        
        \resumeProjectHeading
        {\href{https://projects.anhnlh.com/lofibeats}{\uline{\textbf{LoFiBeats}}} $|$ \emph{C\#, ASP.NET, PostgreSQL, HTML, CSS}}{Jan 2022 -- May 2022}
        \resumeItemListStart
            \resumeItem{Built a music website where users can create playlists, follow other users, and see popular songs among friends.}
            \resumeItem{Scraped song, album, and artist data using the Spotify API to populate the database for the website.}
            \resumeItem{\textbf{Utilized} ASP.NET in C\# for the full-stack development and PostgreSQL for the website database.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


% Custom sections
\section{Leadership}
    \resumeSubHeadingListStart
        \resumeProjectHeading{\textbf{GCCIS Delegate} $|$ \emph{RIT Honors Council}}{Aug 2022 -- Current}
            \resumeItemListStart
                \resumeItem{Leads conversations with professors for cooperative opportunities with the Honors Program.}
                \resumeItem{Communicates with the college advocate to plan recreational and academic activities for students.}
                \resumeItem{Engages in regular Honors Council meetings where officers plan events and discuss concerns within the program.}
            \resumeItemListEnd

        \resumeProjectHeading{\textbf{Orientation Leader} $|$ \emph{Rochester Institute of Technology}}{Aug 2021 -- Aug 2021}
            \resumeItemListStart
                \resumeItem{Led a group of 30 first-year students to attend various events during the university's New Student Orientation.}
                \resumeItem{Facilitated connections and eased the college transition for incoming students through organized group activities.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Awards}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{First Place, Meet \& Hack 2022:} Awarded $1^{st}$ place for the \href{https://github.com/anhnlh/MnT_Health_Website}{\uline{\textbf{HealthHacks}}} website project, out of 13 submissions. \\
        }}
    \end{itemize}


%-------------------------------------------
\ULforem % toggle ulem package emph
\end{document}
